# (PART) Object Visualization {-} 

# `CopyNumber` Object {#cnobject}

## Profile {-}

## Distribution {-}

# `Signature` Object {#sigobject}

`Signature` is a core object in **sigminer**, it stores signatures and their exposures. Here we show how to plot signature profile and exposure profile. The result plots are **ggplot** based, so they can be further edited by your custom operations with **ggplot** grammar.

## Signature Profile {-}

A signature is composed of distinct component patterns. They can be shown by `show_sig_profile()`. Of note, for different types of signature, the bar heights may have different meanings.

- SBS signatures are displayed based on the observed component frequency of the human genome, i.e., representing the relative proportions of mutations generated by each signature based on the actual trinucleotide frequencies of the reference human genome.
- Similar to SBS signatures, copy number signatures are displayed based on the observed component frequency of the human genome. Of note, considering the count process of each feature is relatively independent, the profile is row normalized by each feature, unlike Macintyre et al. (2018) did column normalization (this method is easy to mislead readers), so the bar height can be compared within/between features.

```{r, fig.width=12}
show_sig_profile(mt_sig, mode = "SBS", paint_axis_text = FALSE)
```


```{r, fig.width=12}
show_sig_profile(mt_sig, mode = "SBS", style = "cosmic")
```


## Exposure Profile {-}


```{r, fig.width=12}
show_sig_exposure(mt_sig)
```

```{r, fig.width=12}
show_sig_exposure(mt_sig, style = "cosmic")
```

