# Signature Fit: Sample Signature Exposure Quantification and Analysis {#sigfit}

Besides *de novo* signature discovery shown in previous chapters, another common task is that
you have gotten some reference signatures (either from known database like COSMIC or *de novo* discovery step), you want to know how these signatures contribute (fit) in a sample. That's the target of `sig_fit()`.

`sig_fit()` uses multiple methods to compute exposure of pre-defined signatures from the spectrum of a (can be more) sample. Use `?sig_fit` see more detail.

To show how this function works, we use a sample with maximum mutation counts as example data.

```{r}
i <- which.max(apply(mt_tally$nmf_matrix, 1, sum))

example_mat <- mt_tally$nmf_matrix[i, , drop = FALSE] %>% t()
```

```{r}
head(example_mat)
```


## Fit Signatures from reference databases

For SBS signatures, users may want to directly use reference signatures from COSMIC database.

```{r}
sig_fit(example_mat, sig_index = 1:30)
```
> At default, COSMIC v2 signature database with 30 reference signatures is used (i.e. `sig_db = "legacy"`). Set `sig_db = "SBS"` for COSMIC v3 signature database.

That's it!

You can set `type = "relative"` for getting relative exposure.

```{r}
sig_fit(example_mat, sig_index = 1:30, type = "relative")
```


For multiple samples, you can return a `data.table`, it can be easier to integrate with other information in R.

```{r}
sig_fit(t(mt_tally$nmf_matrix[1:5, ]), sig_index = 1:30, return_class = "data.table", rel_threshold = 0.05)
```

When you set multiple signatures, we recommend setting `rel_threshold` option, which will set exposure of a signature to `0` if its relative exposure in a sample less than the `rel_threshold`.

## Fit Custom Signatures

We have already determined the SBS signatures before. Here we can set them to `sig` option.

```{r}
sig_fit(example_mat, sig = mt_sig2)
```

## Performance Comparison

Now that we can use `sig_fit` for getting optimal exposures, we can compare the RSS between **raw matrix** and the **reconstructed matrix** either by NMF and `sig_fit()`.


i.e. 

$$
RSS = \sum(\hat H - H)^2
$$

```{r}
## Exposure got from NMF
sum((apply(mt_sig2$Signature, 2, function(x) x/sum(x)) %*% mt_sig2$Exposure - t(mt_tally$nmf_matrix))^2)
```

```{r}
## Exposure optimized by sig_fit
H_estimate = apply(mt_sig2$Signature, 2, function(x) x/sum(x)) %*% sig_fit(t(mt_tally$nmf_matrix), sig = mt_sig2)
H_estimate = apply(H_estimate, 2, function(x) ifelse(is.nan(x), 0, x))
H_real = t(mt_tally$nmf_matrix)
sum((H_estimate - H_real)^2)
```


## Estimate Exposure Stability by Bootstrap

This feature is based on `sig_fit()`, it uses the resampling data of original input and runs `sig_fit()` multiple times to estimate the exposure. Bootstrap replicates >= 100 is recommended, here I just use 10 times for illustration.

```{r}
bt_result <- sig_fit_bootstrap_batch(example_mat, sig = mt_sig2, n = 10)
bt_result
```

You can plot the result very easily with functions provided by **sigminer**.

```{r}
show_sig_bootstrap_exposure(bt_result, sample = "TCGA-A8-A09G-01A-21W-A019-09")
show_sig_bootstrap_error(bt_result, sample = "TCGA-A8-A09G-01A-21W-A019-09")
show_sig_bootstrap_stability(bt_result)
```
P values have been calculated under specified relative exposure cutoff (0.05 at default).

The result indicates `Sig3` is very stable.

# Subtype Prediction {#subtyping}

To expand the power of signatures to clinical application, based on **signature discovery** and **signature fitting** workflows, we can go further build neutral network model prediction model with **keras**. This feature is currently experimental and implemented in **sigminer**'s child package [**sigminer.prediction**](https://github.com/ShixiangWang/sigminer.prediction).

# Sigflow Pipeline {#sigflow}

[Sigflow](https://github.com/ShixiangWang/sigflow) provides useful mutational signature analysis workflows based on R package **sigminer**. It can auto-extract mutational signatures, fit mutation data to COSMIC reference signatures (SBS/DBS/INDEL) and run bootstrapping analysis for signature fitting.

For full documentation, please read Sigflow [README](https://github.com/ShixiangWang/sigflow).

## Cancer type specific signature index database

Signature fitting analysis may befit from directly specifying known signatures identified in a cancer type. We collect such information and provide the following data tables.

```{r}
db1 <- system.file("extdata", "cosmic2_record_by_cancer.rds", package = "sigminer")
db1 <- readRDS(db1)
colnames(db1) <- c("Cancer type", "Signature Index")
db2 <- system.file("extdata", "signature_record_by_cancer.rds", package = "sigminer")
db2 <- readRDS(db2)
colnames(db2) <- c("Cancer type", "Cohort", "Sequencing strategy",
                   "SBS signature index",
                   "DBS signature index",
                   "ID signature index")
```

```{r}
DT::datatable(db1, caption = "Data source: https://cancer.sanger.ac.uk/signatures_v2/matrix.png")
```

> Note, set `sig_db` to 'legacy' (the default) in `sig_fit()` family functions.

```{r}
DT::datatable(db2[, c(1:3, 4)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```

```{r}
DT::datatable(db2[, c(1:3, 5)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```

```{r}
DT::datatable(db2[, c(1:3, 6)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```
