# Signature Fit: Sample Exposure Quantification {#sigfit}

Besides *de novo* signature discovery shown in previous chapters, another common task is that
you have gotten a reference signature database (either from known database like COSMIC or *de novo* discovery step), you want to know how these signatures fit in a new sample. That's the target of `sig_fit()`.

`sig_fit()` uses linear combination decomposition to compute exposure of pre-defined signatures from the total
alteration spectrum of a (can be more) sample. Use `?` see more detail.

To show how this function works, we use a sample with maximum mutation counts as example data.

```{r}
i <- which.max(apply(mt_tally$nmf_matrix, 1, sum))

example_mat <- mt_tally$nmf_matrix[i, , drop = FALSE] %>% t()
```

```{r}
head(example_mat)
```


## Fit Signatures from reference databases

For SBS signatures, users may want to directly use reference signatures from COSMIC database. This can be done by specifying the option `sig_index`.



```{r}
sig_fit(example_mat, sig_index = 1:30)
```

That's it!

You can set `type = "relative"` for getting relative exposure.

```{r}
sig_fit(example_mat, sig_index = 1:30, type = "relative")
```


For multiple samples, you can return a `data.table`, it can be easier to integrate with other information in R.

```{r}
sig_fit(t(mt_tally$nmf_matrix[1:5, ]), sig_index = 1:30, return_class = "data.table", rel_threshold = 0.05)
```

When you set multiple signatures, we recommend setting `rel_threshold` option, which will set exposure of a signature to `0` if its relative exposure in a sample less than the `rel_threshold`.

## Fit Custom Signatures

We have already determined the SBS signatures before. Here we can set them to `sig` option.

```{r}
sig_fit(example_mat, sig = mt_sig)
```

## Performance Comparison

Now that we can use `sig_fit` for getting optimal exposures, we can compare the RSS between **raw matrix** and the **reconstructed matrix** either by NMF and `sig_fit()`.


i.e. 

$$
RSS = \sum(\hat H - H)^2
$$

```{r}
## Exposure got from NMF
sum((apply(mt_sig$Signature, 2, function(x) x/sum(x)) %*% mt_sig$Exposure - t(mt_tally$nmf_matrix))^2)
```

```{r}
## Exposure optimized by sig_fit
sum((apply(mt_sig$Signature, 2, function(x) x/sum(x)) %*% sig_fit(t(mt_tally$nmf_matrix), sig = mt_sig) - t(mt_tally$nmf_matrix))^2)
```


