# (PART) Signature Analysis and Visualization {-} 

# Association Analysis and Visualization {#association-analysis}

# Group Analysis and Visualization {#group-analysis}

Group analysis is a common task in cancer study. **sigminer** supports dividing samples into multiple groups and comparing genotype/phenotype feature measures.

## Group Generation {-}

There are multiple methods to generate groups, including 'consensus' (default, can be only used by result from `sig_extract()`), 'k-means' etc. After determining groups, **sigminer** will assign each group to a signature with maximum fraction. We may say a group is `Sig_x` enriched.

```{r, message=TRUE}
mt_grps <- get_groups(mt_sig, method = "consensus", match_consensus = TRUE)
head(mt_grps)
```

The returned sample orders match sample orders in clustered consensus matrix.

```{r}
show_sig_consensusmap(mt_sig)
```


Sometimes, the mapping between groups and enriched signatures may not right. Users should check it and even correct it manually.


```{r}
attr(mt_grps, "map_table")
```


## Group Comparison Analysis {-}

## Group Visualization {-}