# (PART)  Universal Analysis {-} 

# Association Analysis and Visualization {#association-analysis}

## General numeric association

For general numeric association, you can use `show_cor()` function.

```{r}
data("mtcars")
p1 <- show_cor(mtcars)
p2 <- show_cor(mtcars,
               x_vars = colnames(mtcars)[1:4],
               y_vars = colnames(mtcars)[5:8])
p3 <- show_cor(mtcars, vis_method = "circle", p_adj = "fdr")
p1
p1$cor
p2
p3
```

## Comprehensive association

For comprehensive association analysis including both continuous and categorical variables,
there are several functions available in **sigminer**:

- `get_sig_feature_association()`.
- `get_tidy_association()`.
- `show_sig_feature_corrplot()`.

Currently, I haven't provided a proper example dataset for showing usage of all functions above (please read their documentation), here only the tidy dataset from our study [@WangSX2020] is given to show the plot function.

```{r, error=TRUE, fig.height=7, fig.width=6}
# The data is generated from Wang, Shixiang et al.
load(system.file("extdata", "asso_data.RData",
  package = "sigminer", mustWork = TRUE
))

p <- show_sig_feature_corrplot(tidy_data.seqz.feature, p_val = 0.05)
p
```


# Group Analysis and Visualization {#group-analysis}

Group analysis is a common task in cancer study. **Sigminer** supports dividing samples into multiple groups and comparing genotype/phenotype feature measures.

## Group Generation 

There are multiple methods to generate groups, including 'consensus' (default, can be only used by result from `sig_extract()`), 'k-means' etc. After determining groups, **sigminer** will assign each group to a signature with maximum fraction. We may say a group is `Sig_x` enriched.

```{r, message=TRUE}
mt_grps <- get_groups(mt_sig, method = "consensus", match_consensus = TRUE)
head(mt_grps)
```

The returned sample orders match sample orders in clustered consensus matrix.

```{r}
show_sig_consensusmap(mt_sig)
```


Sometimes, the mapping between groups and enriched signatures may not right. Users should check it and even correct it manually.


```{r}
attr(mt_grps, "map_table")
```


## Group Comparison Analysis 

```{r}
load(system.file("extdata", "toy_copynumber_signature_by_M.RData",
  package = "sigminer", mustWork = TRUE
))

# Assign samples to clusters
groups <- get_groups(sig, method = "k-means")

set.seed(1234)

groups$prob <- rnorm(10)
groups$new_group <- sample(c("1", "2", "3", "4", NA), size = nrow(groups), replace = TRUE)

# Compare groups (filter NAs for categorical coloumns)
groups.cmp <- get_group_comparison(groups[, -1],
  col_group = "group",
  cols_to_compare = c("prob", "new_group"),
  type = c("co", "ca"), verbose = TRUE
)

# Compare groups (Set NAs of categorical columns to 'Rest')
groups.cmp2 <- get_group_comparison(groups[, -1],
  col_group = "group",
  cols_to_compare = c("prob", "new_group"),
  type = c("co", "ca"), NAs = "Rest", verbose = TRUE
)
```


## Group Visualization 

```{r}
ggcomp <- show_group_comparison(groups.cmp2)
ggcomp$co_comb
ggcomp$ca_comb
```

