# (PART) Useful Utilities {-} 

# Datasets {#datasets}

## Reference Annotation 

**sigminer** stores many reference annotation datasets for internal calculation. It can be exported for other usage either by `data()` or `get_genome_annotation()`.

Currently, there are the following datasets:

- `centromeres.hg19`
- `centromeres.hg38`
- `chromsize.hg19`
- `chromsize.hg38`
- `cytobands.hg19`
- `cytobands.hg38`

An example is given as below:

```{r}
data("centromeres.hg19")
head(centromeres.hg19)

```


`get_genome_annotation()` can better control the returned `data.frame`.

```{r}
get_genome_annotation(data_type = "chr_size",
                      chrs = c("chr1", "chr10", "chr20"),
                      genome_build = "hg19")
```


More see `?get_genome_annotation`.

## Copy Number components setting 

Dataset `CN.features` is a predefined component data table for identifying copy number signatures by method "Wang".
Users can define a custom table with similar structure and pass it to function like `sig_tally()`.

Detail about how to generate this dataset can be viewed at <https://github.com/ShixiangWang/sigminer/blob/master/data-raw/CN-features.R>.

```{r}
CN.features
```

## SBS Signature Conversion

Converts signatures between two representations relative to different sets of mutational opportunities. Currently, only SBS signature is supported.

```{r, fig.width=12}
# Load SBS signature
load(system.file("extdata", "toy_mutational_signature.RData",
  package = "sigminer", mustWork = TRUE
))
# Exome-relative to Genome-relative
sig_converted <- sig_convert(sig2,
  from = "human-exome",
  to = "human-genome"
)
sig_converted

show_sig_profile(sig2, style = "cosmic")
show_sig_profile(sig_converted, style = "cosmic")
```

