--- 
title: "sigminer: Genomic Alteration Signature Analysis in R"
author:
  - Shixiang Wang, ShanghaiTech University
  - Xue-Song Liu, ShanghaiTech University
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
colorlinks: yes
link-citations: yes
description: "This package helps users to extract, analyze and visualize signatures from genomic variation records, thus providing new insight into cancer study."
github-repo: ShixiangWang/sigminer-doc
---

# Introduction {#intro}

Genomic alterations including single nucleotide substitution (SBS),
copy number variations (CNV), etc. are the major force for cancer
initialization and development.  Due to the specificity of molecular
lesions caused by genomic alterations, we can generate characteristic
variation spectra, called 'signature'. This package helps users to
extract (identify), analyze and visualize signatures from genomic variation records,
thus providing new insight into cancer study.

The **sigminer** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("sigminer")
# or the development version
# devtools::install_github("ShixiangWang/sigminer")
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
